Forecasting biodiversity in breeding birds using best practices

### 2017-12-09 manuscript/reviewer_reply.Rmd

>We agree.

*Line 249: Can you elaborate on what you did with the deviance? By itself mean deviance is just a measure of average fit (I think most of the models are giving you this). Var(deviance) should incorporate precision – but I’ve only seen this extracted from Bayesian models*

*Line 266: I think you guys have done a great job putting together this public repository + made the analysis totally transparent. My one hang up with the repo was that it’d be awesome to include a short vignette with example data from this project that is more easily accessible to readers without having to install Jupyter/R packages/etc. For example – I was travelling when I started this review and couldn’t install one of the R packages on my government computer without making an appointment with our IT staff (so it took ~ a day). This isn’t your fault of course, but much harder for me to dig through the repo.*

>Thanks! We tried to handle this using binder (https://mybinder.org/) to allow anyone to quickly engage with the full environment, but unfortunately the R support isn't quite ready yet. Fortunately it is under active development and as soon as it is available we plan to set it up and link to it from the repository to support this use case.

### 2017-12-09 manuscript/draft.Rmd
Reword sentence that used "forecast" three times in 13 words
equations for baselines

**Future environmental projections.** In addition to the analyses presented
here, we have also generated and archived long term forecasts from 2014-2050.
This will allow future researchers to assess the performance of our six models
on longer time horizons as more years of BBS data become available.
Precipitation and temperature were forecast using the CMIP5 multi-model ensemble
dataset [@brekke2013]. 37 downscaled model runs [@brekke2013, see Table S1]
using the RCP6.0 scenario were averaged together to create a single ensemble
used to calculate the bioclimatic variables for North America. For NDVI, we used
the per-site average values from 2000-2013 as a simple forecast. For observer
effects (see below), each site was set to have zero observer bias. The
predictions have been archived at [@zenodoPredict].

@@

**Baseline models.** We used two simple baseline models as a basis for
comparison with the more complex models (Figure 2A). These baselines treated
site-level richness observations either as uncorrelated noise around a
site-level constant (the "average" model) or as an autoregressive model with a
single year of history [the "naive" model, @hyndman2014]. Predictions from the
"average" model are centered on the average richness observed during training,
and the confidence intervals are narrow and constant-width. The "naive" model,
in contrast, predicts that future observations will be similar to the final
observed value (e.g., in our hindcasts the value observed in `r
timeframe$last_train_year`), and the confidence intervals expand rapidly as the
predictions extend farther into the future. Both models' richness predictions
are centered on a constant value, so neither model can anticipate any trends in
richness or any responses to future environmental changes.

>>>>

**Future environmental projections.** We made long term forecasts from 2014-2050
using the CMIP5 multi-model ensemble dataset as the source for climate
variables [@brekke2013]. Precipitation and temperature from 37 downscaled model
runs [@brekke2013, see Table S1] using the RCP6.0 scenario were averaged
together to create a single ensemble used to calculate the bioclimatic variables
for North America. For NDVI we used the per-site average values from 2000-2013
as a simple forecast. For observer effects (see below) each site was set to have
zero observer bias.

@@

**Baseline models.** We used two simple baseline models as a basis for
comparison with the more complex models (Figure 2A). The first baseline, called
the "average" model, treated site-level richness observations as uncorrelated
noise around a site-level constant:

$$y_t = \mu + \epsilon_t.$$

Predictions from the "average" model are centered on the average richness
observed during training, and the confidence intervals are narrow and
constant-width.

The second baseline, called the "naive" model [@hyndman2014], was a simple
autoregressive process with a single year of history:

$$y_t = y_{t-1} + \epsilon_t$$

In contrast to the "average" model, whose predictions were based on the average
richness across the whole time series, the "naive" model predicts that future
observations will be similar to the *final* observed value (e.g., in our
hindcasts the value observed in `r timeframe$last_train_year`), and the
confidence intervals expand rapidly as the predictions extend farther into the
future. Both models' richness predictions are centered on a constant value, so
neither model can anticipate any trends in richness or any responses to future
environmental changes.
